Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-11-26 presentacion_hiram/presentacion-tesis.tex
new
Fix bug
n

\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{array}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{multicol}
\usepackage{listings}
\usepackage{alltt}
\usepackage{mathtools}
\usepackage[makeroom]{cancel}
\usetheme{Frankfurt}
\usepackage{tikz} 
\usetikzlibrary{patterns}
\usetikzlibrary{plotmarks}
\titlegraphic{\vspace{8cm}}% to push the other text to the top
\addtobeamertemplate{navigation symbols}{}{%
	\usebeamerfont{footline}%
	\usebeamercolor[fg]{footline}%
	\hspace{1em}%
	\insertframenumber/\inserttotalframenumber
	\setbeamercolor{footline}{fg=blue}
	\setbeamerfont{footline}{series=\bfseries}
}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
		\newcommand\Fontvi{\fontsize{4}{7.2}\selectfont}
\begin{document}
	\author{\tiny
			L.F. Hiram Ernesto Dami\'an\\
			\vspace{5px}
				Director:\\
					\vspace{5px}
			Jos\'e Feliciano Ben\'itez Rubio\\
				\vspace{5px}
				Maestr\'ia en Ciencias (F\'isica)\\
					\vspace{5px}
			 Departamento de Investigacion en F\'isica }
	\title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
	%\subtitle{}
	\logo{\includegraphics[scale=0.1]{unison-logo.png}}
	\newcommand{\nologo}{\setbeamertemplate{logo}{}}
	\institute{Universidad de Sonora}
	\date{\small November 15$^{th}$ 2019}
	%\subject{}
	\newcommand{\subf}[2]{%
		{\small\begin{tabular}[t]{@{}c@{}}
				#1\\#2
		\end{tabular}}%
	}
	%\setbeamercovered{transparent}
	%\setbeamertemplate{navigation symbols}{}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\tiny
\tableofcontents
\end{frame}

%\begin{frame}
%\section{Overview and motivation}
%\frametitle{Overview}
%\begin{itemize}
%\item Through this project it was studied the production of Higgs boson in association with a
%single top quark ($tH$) in proton-proton collisions. 
%This mechanism of production of the Higgs boson has not been observed before by any
%experiment.
%\item Standard Model and the Higgs production mechanism
%\item A brief introduction to the LHC and CMS
%\item Event selection and reconstruction of the tH signal
%\item Creation and application of a statistical model for the analysis of events 
%\item Making predictions for the future experiments.
%\end{itemize}
%\end{frame}

\begin{frame}
\frametitle{Motivation  for single top Higgs (tH)}
\begin{itemize}
\item Coupling measurement is essential to establish the nature of the Higgs
\item The exploration of Higgs production on the $tH$ channel is subject relatively new. Measurements of CMS and ATLAS are compatible with SM predictions.
\item The $tH$ study explores the relative sign of top-Higgs  and W-Higgs couplings.\\ Small deviations from SM predictions could be associated with physics beyond the
standard model (BSM) such as String Theory and  Supersymmetry.
\end{itemize}
\end{frame}

\begin{frame}
\section{Introduction}
\subsection{Standard Model}
\frametitle{Standard Model}
\begin{table}
	\centering
\begin{tabular}{cc}
\includegraphics[width=6cm,height=5cm]{figures/sm1.png} & \includegraphics[width=5cm,height=5cm]{figures/sm.png}
\end{tabular}
\end{table}
\end{frame}

\begin{frame}
\frametitle{Particles Properties}
Table of particles in SM
\begin{table}
\tiny{\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c|c|c|c|p{2.5cm}|}
\hline 	
Particle	& Mass (MeV/$c^2$) &Charge & spin &Lifetime (s) & Distance in lifetime (meters) \\ 
\hline 
Up ($u$)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & stable & -\\ 
\hline 	
Charm ($c$)	& 1280 &$\frac{2}{3}$ & $\frac{1}{2}$ & $ 1.1 \times 10^{-12}$ & 5.21$\times 10^{-3}$ \\ 
\hline 
Top	($t$)& 173100 & $\frac{2}{3}$ & $\frac{1}{2}$ & 5$\times$10$^{-25}$ &2.37$\times 10^{-15}$  \\ 
\hline 
Down ($d$)	& 4.6 &$-\frac{1}{3}$ & $\frac{1}{2}$ & Stable & - \\ 
\hline 
Strange ($s$)	& 96 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.24 \times 10^{-8}$ & 58.7 \\ 
\hline 
Bottom ($b$)	& 4180 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.3 \times 10^{-12}$  & 6.16 $\times 10^{-3}$\\ 
\hline 
$W$ 	& 80379 &$\pm$1 & 1 & 3$\times$ 10$^{-25}$ & 1.42$\times 10^{-15}$\\ 
\hline 
$Z$ & 91187.6 &0 & 1 & 3$\times$ 10$^{-25}$ &1.42$\times 10^{-15}$ \\ 
\hline
Photon ($\gamma$) & 0 &0 & 1&Stable & - \\ 
\hline
Gluon ($g$)	& 0 &0 & 1&Stable & - \\ 
\hline 
Higgs ($H$)	& 125.18 &0 & 0& 1.56 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
\hline 
Electron ($e$)& 0.511 & -1 &  $\frac{1}{2}$& Stable & - \\ 
\hline 
Muon ($\mu$)	& 105.7 & -1 & $\frac{1}{2}$ & 2.2$\times$10$^{-6}$ & 10419.85 \\ 
\hline 
$\tau$	& 1776.86 &-1 & $\frac{1}{2}$ & 2.9$\times$10$^{-13}$ & 1.37$\times 10^{-3}$\\ 	
\hline 
$\nu_e$	$\nu_\mu$ $\nu_\tau$& 0 & 0 & $\frac{1}{2}$ & Stable & -\\
\hline 
\end{tabular} 
}
\end{table}
\tiny{Stable means no decay, or lifetime almost infinite. Particles speeds at 0.998c}
\end{frame}

%\begin{frame}
%\subframetitle{Higgs mechanism}
%\frametitle{Electroweak SM Lagrangian}
%The Standard Model is a theory of fields for particles with spins 0, $\frac{1}{2}$ and 1. 
%The  SM lagrangian 	
%\begin{align*}
%\mathcal{L}=\mathcal{L}_\text{gauge}+\mathcal{L}_f +\mathcal{L}_\text{higgs} + \mathcal{L}_\text{yukawa}
%\end{align*}
%donde 
%\begin{itemize}
%	\item $\mathcal{L}_\text{gauge}$=$ -\frac{1}{4}\left[F^{\mu\nu}F_{\mu\nu}\right]-\frac{1}{4}\left[G^{i\mu\nu}G^i_{\mu\nu}\right]$ 
%	\begin{itemize}
%		\item  $F^{\mu \nu}=\partial_\mu B_\nu -\partial_\nu B_\mu $
%		\item  $G^{i\mu\nu}=\partial_\mu W^i_\nu -\partial_\nu W^i_\mu -g\epsilon^{ijk}W^j_\mu W^k_\nu $
%	\end{itemize}
%	\item $\mathcal{L}_f=i\bar{\Psi}_L \cancel{D}{\Psi}_L+i\bar{\psi}_R \cancel{D}{\psi}_R  $ is the kinematic term for fermions 
%\scriptsize{
%	\begin{itemize}
%		\item $D_\mu {\Psi}_L=\left(\partial_\mu+igW_\mu+ig'Y_LB_\mu\right)\Psi_L$
%		\item $D_\mu \psi_R=\left(\partial_\mu +ig' Y_RB_\mu\right)\psi_R $
%		\item g and g' are boson coupling constants.
%\footnote{\tiny{L(R) refers to Left and right fields.
%Y is the  weak hypercharge,Y=T$^3$-Q.Q is charge of particle field and T is weak isospin. $T^3=\pm 1/2$ for left handed doublets and $T^3=0$ for right handed singlets.} }
%\item $W_\mu=\sigma^iW^i_\mu$, where $\sigma^i$ are the pauli matrices.
%	\end{itemize}
%}
%\end{itemize}
%\begin{equation}
%\begin{split}
%\mathcal{L}=-\frac{1}{2}\text{Tr}\left[F^{\mu\nu}F_{\mu\nu} \right]+\bar{\Psi_L}i\gamma^\mu D_\mu \Psi_L  
%+\text{Tr}\left[(D_\mu \Phi)^\dagger (D^\mu \Phi)\right]+\mu^2 \Phi^\dagger \Phi  \\
%-\frac{1}{2}  \lambda (\Phi^\dagger \Phi)^2 & +\left(\frac{1}{2}\Psi_L^T Ch \Phi \Psi_L +h.c \right)
%\end{split}
%\end{equation}
%The matrix C in the last term is the charge conjugation matrix acting on the spinors, h is a matrix of Yukawa couplings
%\end{frame}

\begin{frame}
\subsection{Higgs mechanism}
\frametitle{Electroweak SM Lagrangian}
Higgs lagrangian 
\begin{align}
\mathcal{L}_{\text{Higgs}}=(D_\mu \Phi)^\dagger (D^\mu \Phi)-V(\Phi^\dagger \Phi)
\end{align}

with
\begin{itemize}
	\item $D_\mu \Phi = \left(\partial_\mu+(ig/2)\sigma^iW^i_\mu-i\frac{1}{2} g' B_\mu \right) \Phi $
	\item $V(\Phi^\dagger \Phi)=-\mu^2 \Phi^\dagger \Phi +\frac{1}{2}  \lambda (\Phi^\dagger \Phi)^2, \quad \mu^2>0  $ 
	\item $\Phi=\left(\begin{array}{c}
	\phi^+ \\
	\phi^0
	\end{array} \right)  $ is a SU(2) doublet.
	\item $\sigma^i$ are the Pauli matrices.
\end{itemize}

\begin{itemize}
	\item $\Phi$ is higgs field which is a complex scalar field. $\Phi$
	%\item  W$_\mu$ and B$_\mu$ are gauge bosons
	%\item g and g are boson coupling constants.
	\item $\lambda $ and $\mu^2$ are Higgs potential parameters
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{SM Lagrangian}
Yukawa lagrangian
\begin{align}
\mathcal{L}_\text{yukawa}=\sum_{m,n}^{3}  \Gamma^u_{mn}\bar{q}_{m\text{,}L} \tilde{\Phi} u_{n\text{,}R}%+\Gamma^d_{mn}\bar{q}_{m\text{,}L} \Phi d_{n\text{,}R}+\Gamma^e_{mn}\bar{l}_{m\text{,}L} \Phi e_{n\text{,}R}+h.c
\end{align}
\scriptsize{where h.c is hermitian conjugate. m and n are flavors of quarks and leptons.
\\
The matrices $\Gamma_{mn}$ describe the so called Yukawa couplings between higgs doublet $\phi$ and the fermions.\\
Choosing}
\begin{align*}
\Phi=-\frac{1}{2}\left(\begin{array}{c}
0 \\
v+h
\end{array} \right) \label{vmin}
\end{align*}
\scriptsize{
By using \ref{vmin} it on $\mathcal{L}_\text{yukawa}$, it is obtained for $u$ quark
\begin{align*}
\frac{\Gamma^u_{uu}v}{\sqrt{2}}(\bar{u_L}u_R+\bar{u_R}u_L)
\end{align*}
from which the masses for the fermions shown to be proportional to the Yukawa couplings
\begin{align*}
m_u=-\frac{\Gamma^u_{uu}v}{\sqrt{2}}
\end{align*}}
\end{frame}

{\nologo
\begin{frame}
\subsection{Higgs production mechanisms and decays}
\frametitle{Higgs production mechanisms}

\begin{center}
\includegraphics[scale=0.4]{figures/pg.png}
\end{center}
\small{Different Higgs production mechanism, from the most likely to least likely}
\end{frame}
}

{\nologo
\begin{frame}
\frametitle{$tH$ production mechanisms}
\begin{center}
\begin{figure} 
\includegraphics[scale=0.4]{figures/tq.png} 
\caption*{$tH$ mechanism. Higgs radiated from a top quark (left). Higgs radiated from a W boson (right)} 
\label{th}
\end{figure}
\end{center}
\end{frame} 
}

\begin{frame}
\frametitle{$tH$ production mechanisms}
\begin{itemize}
\item In a proton proton collision, the production cross section of the single top plus Higgs boson process is driven by a
destructive interference of two main diagrams, where the Higgs couples to either
the W boson or the top quark. 
\item  A second process, where the Higgs and top quark
are accompanied by a W boson ($tH$W) has similar behavior, albeit with a weaker interference
pattern.
\item However, in the presence of new physics, there may be relative opposite signs between the $tH$
and WH couplings which lead to constructive interference and enhance the cross sections by
an order of magnitude or more.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Cross section}
\begin{itemize}
\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
\item Experimentally
\begin{align}
d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
\end{align}
\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$ 
\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
L is called luminosity and it is measured in cm$^{-1}$s$^{-1}$.\cite{6}
\begin{align}
N_R=\sigma \text{L}
\end{align}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Higgs production Cross section}
\begin{table}
	\caption*{Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in
		pico barn).Integrated luminosity of 35.9 fb$^{-1}$ for Run 2\footnotemark}
	\begin{tabular}{|c|c|c|}
		\hline
		Production mechanism &
		$\sigma$ (picobarns pb)
		&Number of events \\
		\hline
		ggF &
		48.93 &
		1756587\\
		\hline
		VBF &
		3.78&
		135702\\
		\hline
		WH & 1.35 & 48465\\
		\hline
		ZH &0.88 & 31592\\
		\hline
		t$\bar{t}$H &
		0.50&
		18255\\
		\hline
		$tH$	(only)&
		0.015&
		560.39\\
		\hline
	\end{tabular}
\end{table}

\footnotetext[1]{\tiny{Data taken from The cern collaborarion “Higgs Physics the HL-LHC and HE-LHC” 2019, CERN-LPCC-2018-04}}

\end{frame}

\begin{frame}
\frametitle{Branching ratio}
\small{In particle physics, the branching ratio for a decay process is the ratio of the number of particles which decay via a specific decay mode with respect to the total number of particles which decay via all decay modes. \footnotemark.}
\begin{align}
\text{BR} =\frac{\Gamma_i}{\sum_{i}\Gamma_i}
\end{align}
\small{Where $\Gamma=\sum_i\Gamma_i$ is the total decay width (sum of all partial widths) of the particle and is related to lifetime of the particle: $\Gamma=1/\tau$.
Since the dimension of $\Gamma$ is the inverse of time, in our system of natural units, it is measured in inverse seconds} .%it has the same dimension as mass (or energy).}
\footnote[0]{\tiny{Cleaves H.J. (2011) Branching Ratio. In: Gargaud M. et al. (eds) Encyclopedia of Astrobiology. Springer, Berlin, Heidelberg} }
\end{frame}

\begin{frame}
\frametitle{Higgs Branching ratios per channel}
\begin{table}
	\caption*{SM Higgs boson branching ratios for  $M_H$ =125 GeV}
\begin{center}
\begin{tabular}{|c|c|}
	\hline
	Higgs decay & Branching ratio (BR)\\
	\hline
	H $\rightarrow$ b$\bar{b}$ &
	$50.82\%$ \\
	\hline
	H $\rightarrow$ $W^+W^-$ &
	$21.5\%$ \\
	\hline
	H $\rightarrow$ $\tau^+ \tau^-$ &
	$6.27\%$\\
\hline
	H $\rightarrow$ ZZ &
$2.61\%$\\
\hline
	H $\rightarrow$ $\gamma\gamma$ &
$0.227\%$\\
\hline
	H $\rightarrow$ Z$\gamma$ &
$0.153\%$\\
\hline
	H $\rightarrow$ $\mu^+\mu^-$ &
$0.0217\%$\\
\hline
\end{tabular}
\end{center}
\end{table}

\end{frame}

\begin{frame}
\frametitle{$\mu\mu$ same sign decay rate}
\tiny{Table of decay chains for tH.  Expected number of $tH$ final states events for 35.9 fb$^{-1}$.l represents $\mu^{\pm},e^- , \tau^\pm$. }
\begin{table}
\renewcommand{\arraystretch}{0.55}
\begin{tabular}{|p{8cm}|p{1.3cm}|c|}
\hline
Decay chain &BR&Events\\
\hline 
\tiny{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+$ $\nu_\mu$b$\mu^+\nu_\mu$  $q \bar{q}'$ } &\tiny{2.096 $\times$10$^{-3}$} &  1.173  \\
\hline
\tiny{$tH \rightarrow $W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+\nu_\mu$b$\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\tiny{3.37 $\times$ 10$^{-4}$} &0.899 \\
\hline
\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu$ b $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\tiny{3.637$\times$10$^{-4}$}&0.203 \\
\hline
\tiny{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b $\mu^+ \nu_\mu$  $q\bar{q}$ $\rightarrow$ $\mu^+ \nu_\mu$ $\bar{\nu_\tau}$ $\bar{\nu_\tau}$ b$\mu^+ \nu_\mu$  $q \bar{q}$} &\tiny{1.890$\times$10$^{-4}$}&0.105  \\
\hline
\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+$ $\nu_\mu$b $\nu_\tau$ $\mu^+$ $\nu_\mu \bar{\nu_\tau}$} $q \bar{q}$  &
\tiny{1.681 $\times$10$^{-4}$} & 0.094 \\
\hline
\tiny{$tH \rightarrow$ W$^+$b W$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$ $\rightarrow$ $\mu^+\nu_\mu$ $ \bar{\nu_\tau} \bar{\nu_\tau}$  b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$} &\tiny{3.045$\times$10$^{-5}$}& 0.017\\
\hline
\tiny{$tH \rightarrow$ W$^+$bZZ $\rightarrow$ $q \bar{q}$bZZ $\rightarrow$ $q \bar{q} $ b $\mu^+ \mu^- \mu^+ \mu^-$} & \tiny{1.966$\times$10$^{-5}$} &0.011\\
\hline 
\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ $\rightarrow$  $\mu^+ \nu_\mu \bar{\nu_\tau}\bar{\nu_\tau} $b $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ } &\tiny{1.549 $\times$10$^{-5}$} &  0.008  \\
\hline
%\tiny{$tH \rightarrow$W$^+$bZ$\gamma$ $\rightarrow$ $\mu^+ \nu_\mu$ b $\mu^+ \mu^- \gamma$} & \tiny{6.888$\times$10$^{-6}$}&0.003\\
%\hline 
%\tiny{$tH \rightarrow$W$^+$bZZ $\rightarrow$ $\mu^+ \nu_\mu$ b $\mu^+ \mu^- l^+l^-$} &\tiny{3.962$\times$10$^{-6}$ }&0.002\\
%\hline 
%%\tiny{$tH \rightarrow$ $\tau \nu_\tau $bZ$\gamma$ $\rightarrow$ $\mu^- \bar{\nu_\mu} \nu_\tau \nu_\tau$ b $\mu^+ \mu^- \gamma$} & 6.347$\times$10$^{-7}$ & 0.0003\\
%%\hline 
\end{tabular}
\end{table}
\end{frame}

\begin{frame}
\section{LHC and CMS}
\subsection{LHC}
\frametitle{LHC}
	\begin{figure}
		\centering
	\includegraphics[scale=0.2]{figures/CERN's-accelerator-complex2013.jpg}
	\caption*{LHC complex}
	\end{figure}
\end{frame}

\begin{frame}
\frametitle{LHC}
\begin{figure}
	\centering
	\includegraphics[scale=0.6]{figures/lhc-u.png}
	\caption*{Underground view of LHC complex}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{LHC parameters}
\begin{minipage}[c]{0.48\textwidth}
	\tiny
\begin{table}
	\caption*{Characteristics of LHC}
\centering
\begin{tabular}{|c|c|}
			\hline
			Quantity & Number \\
			\hline
			Circumference &  26 659 m \\
			\hline
			Number of magnets& 9593 \\
			\hline
			Nominal energy, protons & 6.5 TeV\\
			\hline
			Nominal energy, protons collisions &  13 TeV\\
			\hline
			Number of collisions per second &1 billion\\
			\hline
			No. of bunches per proton beam &  2808\\
			\hline
\end{tabular}
\end{table}
\end{minipage}
\hfill
\begin{minipage}[c]{0.48\textwidth}
	\tiny
	\begin{table}
		\centering
		\caption*{Accelerator operation energies}
		\begin{tabular}{|c|c|}
			\hline
			Accelerator & Energy \\
			\hline
			Linac 2 &  50 MeV \\
			\hline
			PS Booster & 1.4 GeV \\
			\hline
			Proton Scyncroton (PS) & 25 GeV\\
			\hline
			SPS &  450 GeV\\
			\hline
			LHC & 6.5 TeV\\
			\hline
		\end{tabular}
	\end{table}
\end{minipage}
\end{frame}

\begin{frame}
\subsection{CMS dectector}
\frametitle{CMS detector}
\begin{center}
	\begin{figure}
		\includegraphics[scale=0.08]{figures/cms.png}
		\caption*{Compact muon solenoid}
	\end{figure}
\end{center}
\end{frame}

\begin{frame}
\frametitle{CMS detector}
\begin{figure}[ht!]
	\centering
	\includegraphics[scale=0.6]{figures/csc.png}
	\caption*{Slide view of the CMS in terms of pseudorapidity $\eta=-\ln\left[\tan\left(\frac{\theta}{2}\right)\right]$}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{CMS detector}
\begin{figure}
	\centering
	\includegraphics[scale=0.4]{figures/pp.png}
	\caption*{\small A typical CMS event display of the Higgs boson decaying to four leptons with 2 muons (in red) and 2 electrons (in green) as final state signatures.}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{CMS integrated luminosity}
\begin{center}
	\begin{figure}
		\includegraphics[scale=0.3]{figures/cms_lumi.png}
		\caption*{Integrated luminosity for CMS experiment }
	\end{figure}
\end{center}
\end{frame}

\begin{frame}
\section{Event selection and reconstruction}
\subsection{Topology of $tH$}
\frametitle{Topology of events tH}
The characteristics of the signal $tH$:

\begin{multicols}{2}
	\small{
\begin{itemize}
\item $t\rightarrow W$$^+$b$\rightarrow$ $l^+ \nu_\mu b$
\item $H\rightarrow$ $W^+$$W^-$

\begin{list}{--}{}
\item  \small{$W\rightarrow$ $l^\pm \nu$, where $l$ can be $\mu^\pm$,$e^-$  $\tau^\pm$} 
\item   \small{$W\rightarrow$ $q\bar{q}$}
\item \small{$W$ bosons decay leptonically resulting in a signature of two same-sign leptons }
\end{list}
\item a light-flavor quark 
\item  A b-jet  
\end{itemize}
}
\columnbreak
\begin{figure}
	\centering
	\includegraphics[scale=0.5]{figures/jet.png}
\end{figure}
\end{multicols}
\end{frame}

%\begin{frame}
%\frametitle{Backgrounds}
%\subsection{Backgrounds}
%\begin{itemize}
%	\item Backgrounds are considered information in the data that is not the signal. 
%	\item Backgrounds share certain characteristics of the signal.
%	\item Backgrounds are a big factor in the statistical study of the signal.
%\end{itemize}
%\end{frame}

>>>>

#include "minimize.C"
#include "ModelInfo.C"

#include "RooMinimizerFcn.h"
#include "RooRealVar.h"

#include "TGraph.h"
#include "TAxis.h"
#include "TString.h"
#include "TLine.h"

#include <iostream>

using namespace std;

void scanLikelihood(string version, string parName="mu", double range=2, int nrPoints=20)
{
  //Use a convenient helper struct to make opening the workspace and grabbing the objects easier
  //See macros/ModelInfo.C
  ModelInfo info(Form("_combined_%s_model.root",version.c_str(),version.c_str()),
		 "combined",
		 "ModelConfig",
		 "obsData");

  //Grab the parameter you want to scan the NLL over
  RooArgSet params(*info.mc->GetNuisanceParameters(),*info.mc->GetParametersOfInterest());
  RooRealVar* par = info.w->var(parName.c_str());
  if (!par)
  {
    cout << "ERROR::Parameter doesn't exist: " << parName << endl;
    params.Print("v");
    exit(1);
  }

  //Configure MINUIT
  ROOT::Math::MinimizerOptions::SetDefaultMinimizer("Minuit2");
  ROOT::Math::MinimizerOptions::SetDefaultStrategy(0);
  ROOT::Math::MinimizerOptions::SetDefaultPrintLevel(1);

  //Make sure your parameters are floating
  TIterator* itr = params.createIterator();
  RooRealVar* var;
  while ((var=(RooRealVar*)itr->Next()))
  {
    var->setConstant(0);
  }

  //Build the NLL
  RooNLLVar* nll = (RooNLLVar*)info.mc->GetPdf()->createNLL(*info.data, Constrain(params),
							    GlobalObservables(*info.mc->GetGlobalObservables()),
							    RooFit::Offset(1));

  //Do an unconditional fit (all parameters floating)
  minimize(nll);

  //Save the value of the NLL and the best fit value of the parameter at this point
  double nll_best = nll->getVal();
  double muhat = par->getVal();

  //Instantiate the arrays you'll use to save the scanned points
  double* x_ary = new double[nrPoints+1];
  double* y_ary = new double[nrPoints+1];

  //Loop over each point in the scan, do a dit, and save the NLL and the parameter point
  int counter=0;
  bool passedMinimum = false;
  for (int i=0;i<nrPoints;i++)
  {
    //Value of the parameter at this point in the scan
    //double val = muhat - range + i / double(nrPoints-1) * 2*range;
    double xmin=0;
   double xmax=40;

 double val= i*(xmax-xmin)/nrPoints;
    //Save the unconditional point we had earlier at the appropriate point in the array
    if (val > muhat && !passedMinimum)
    {
      passedMinimum = true;
      x_ary[counter] = muhat;
      y_ary[counter] = 0;
      counter++;
    }

    //Fix the parameter to its point in the scan and do the fit there
    par->setVal(val);
    par->setConstant(1);
    minimize(nll);

    //Save the -2*log(L(par) / L(par_hat))
    double dnllx2 = 2*(nll->getVal()-nll_best);
    x_ary[counter] = val;
    y_ary[counter] = dnllx2;
    counter++;
    cout << "On point " << i+1 << " / " << nrPoints << ". " << parName << "=" << val << ", -2lnLambda=" << dnllx2 << " (best fit = " << muhat << ")" << endl;
  }

  //Graph the results
  TCanvas *cs = new TCanvas("cs","cs",10,10,1200,900);
  TGraph* graph = new TGraph(nrPoints+1, x_ary, y_ary);
  graph->Draw("alp*");
  graph->GetXaxis()->SetTitle(parName.c_str());
  graph->GetYaxis()->SetTitle("-2 ln #lambda(#mu)");
 graph->SetTitle();
 graph->GetXaxis()->SetLimits(0,50);
 graph->GetYaxis()->SetRangeUser(0,10);
 graph->Draw("lp*");

  TLine l;
  l.SetLineStyle(2);
  l.SetLineWidth(2);
  l.SetLineColor(kRed);
  l.DrawLine(0,1,50,1);
  l.SetLineColor(kBlue);
  l.DrawLine(0,4,50,4);
  l.SetLineColor(kGreen+4);
  l.DrawLine(0,9,50,9);

TLatex lat ;
lat.SetTextSize(0.03);
lat.DrawLatex(45,1,"1#sigma (68.9#/%");

TLatex lat2;
lat.SetTextSize(0.03);
lat.DrawLatex(45,4,"2#sigma");
lat.DrawLatex(45,9,"3#sigma");

cs->SaveAs("Likelihood.png");
//cs->SaveAs("Likelihood-kt-1.png");

/////////////////////////////////////////////////////////
TCanvas *tm1 = new TCanvas("tm1","tm1",100,100,1200,900);
tm1->Range(0,0,10,1);
TH1F *hoto = new TH1F("hoto",";t_{#mu};f(t_{#mu})",1,0,10.9);
TF1 *fa2 = new TF1("fa2","((1/sqrt(2.*pi))*(1/sqrt(x))*exp(-x/2.))",0,10);
//fa2->SetParameters(x_ary);
//fa2->SetTitle(" p-value for t_{#mu}  k_{t}=1 ;t_{#mu};P(t_{#mu})");
hoto->SetStats(0);
fa2->SetTitle();
fa2->SetLineColor(kBlack);
hoto->Draw();
hoto->GetXaxis()->SetRangeUser(0,10.9);
hoto->GetYaxis()->SetRangeUser(0,1.1);
fa2->DrawIntegral("same");

TF1 *fa3 = new TF1("fa3","((1/sqrt(2.*pi))*(1/sqrt(x))*exp(-x/2.))",0,10);
fa3->SetLineColor(kBlue);
fa3->Draw("same");
///////////////////////////////////////////
TLine l2;
l2.SetLineStyle(2);
l2.SetLineWidth(2);
l2.SetLineColor(kRed);
l2.DrawLine(1,0,1,1);
l2.SetLineColor(kBlue);
l2.DrawLine(4,0,4,1);
l2.SetLineColor(kGreen+4);
l2.DrawLine(9,0,9,1);
lat.DrawLatex(1,1,"1#sigma");
lat.DrawLatex(4,1,"2#sigma");
lat.DrawLatex(9,1,"3#sigma");
//////////////////////////////////////////////////////
TArrow *ar1 = new TArrow(0,-0.03,1,-0.03,0.008,"<>");
lat2.SetTextSize(0.03);
lat2.SetTextColor(2);
lat2.DrawLatex(0.32,-0.1,"68.3%");
ar1->SetLineColor(2);
ar1->Draw();
///////////////////////////////////////////////////////
TArrow *ar2 = new TArrow(0,-0.05,4,-0.05,0.01,"<>");
ar2->SetLineColor(4);
ar2->Draw();
lat2.SetTextSize(0.03);
lat2.SetTextColor(4);
lat2.DrawLatex(4.32,-0.1,"95.4%");
////////////////////////////////////////////////////////
TArrow *ar3 = new TArrow(0,-0.07,9,-0.07,0.01,"<>");
ar3->SetLineColor(kGreen+4);
ar3->Draw();
lat2.SetTextSize(0.03);
lat2.SetTextColor(kGreen+4);
lat2.DrawLatex(9.32,-0.1,"99.7%");

TGaxis *axis5 = new TGaxis(10.9,0,10.9,1.1,0,1.1,510,"+L");
//axis5->SetLabelFont(0.5); // Absolute font size in pixel (precision 3)
axis5->SetLabelSize(0.04);
axis5->SetTitle("P_{#mu}");
axis5->Draw();

cout<<fa3->Integral(0,4)<<endl;

tm1->SaveAs("nos.png");

//TCanvas *tm2 = new TCanvas("tm2","tm2",100,100,1200,900);
//fa2->SetLineColor(kRed);
//fa2->SetTitle();
//fa2->GetXaxis()->SetTitle("t_{#mu}");
//fa2->GetYaxis()->SetTitle("f(t_{#mu})");
//fa2->GetXaxis()->SetLimits(0,10);
//fa2->Draw();
//tm2->SaveAs("tmu.png");

}
